Insert the article title here

### 2018-08-08 writeup/manuscript.tex
Fixing some references.

I think he sees it as a positive thing that they tasks don't correlate, because ti suggests they capture unique variation in behaviour
glass half full approach

@@

>>>>

I think he sees it as a positive thing that they tasks don't correlate, because it suggests they capture unique variation in behaviour
glass half full approach

@@

Mention \cite{stoet2011}.
